















% ------------------------------------------------------------------------------
% Bibliography
% ------------------------------------------------------------------------------
%\bibliography{article}{}
%\bibliographystyle{plain}

\begin{thebibliography}{10}

\bibitem{avigad}
Jeremy Avigad, Edward Dean, and John Mumma.
\newblock A formal system for {E}uclid's \emph{{E}lements}.
\newblock {\em Review of Symbolic Logic}, 2(4):700--768, 2009.

\bibitem{locales}
Clemens Ballarin.
\newblock Interpretation of locales in isabelle: Theories and proof contexts.
\newblock In {\em MKM}, LNCS 4108, pp.~31--43. Springer, 2006.

\bibitem{buchberger}
Bruno Buchberger.
\newblock Bruno Buchberger's PHD thesis 1965: An algorithm for finding the
  basis elements of the residue class ring of a zero dimensional polynomial
  ideal.
\newblock {\em J. Symb. Comput.}, 41(3-4):475--511, 2006.


\bibitem{hilbert-coq}
Christophe Dehlinger, Jean-François Dufourd and Pascal Schreck.
\newblock Higher-Order Intuitionistic Formalization and Proofs in Hilbert’s Elementary Geometry.
\newblock In {\em Automated Deduction in Geometry}, ADG'01, LNCS 2061, Springer. 2001.



\bibitem{grassman}
Laurent Fuchs and Laurent Th{\'e}ry.
\newblock A formalization of Grassmann-Cayley algebra in COQ and its
  application to theorem proving in projective geometry.
\newblock In {\em Automated Deduction in Geometry}, ADG'10, pp.~51--67. Springer. 2011.

\bibitem{wucoq}
Jean-David G{\'e}nevaux, Julien Narboux, and Pascal Schreck.
\newblock Formalization of Wu's simple method in COQ.
\newblock In {\em CPP}, LNCS 7086, pp.~71--86. Springer, 2011.

\bibitem{grobnercoq}
Benjamin Gr{\'e}goire, Lo\"{\i}c Pottier, and Laurent Th{\'e}ry.
\newblock Proof certificates for algebra and their application to automatic
  geometry theorem proving.
\newblock In {\em Automated Deduction in Geometry}, LNCS 6301, pp.~42--59. Springer, 2011.

\bibitem{guilhot}
F.~Guilhot.
\newblock Formalisation en COQ et visualisation d’un cours de g\'eom\'etrie
  pour le lyc\'e.
\newblock {\em TSI 24, 1113–1138}, 2005.


\bibitem{wlog}
John Harrison.
\newblock Without loss of generality.
\newblock In {\em TPHOLs}, LNCS 5674, pp.~43--59. Springer, 2009.

\bibitem{hilbert}
David Hilbert.
\newblock {\em Grundlagen der Geometrie}.
\newblock Leipzig, B.G. Teubner, 1903.

\bibitem{isabelle-quotient}
Cezary Kaliszyk and Christian Urban.
\newblock Quotients revisited for Isabelle/HOL.
\newblock In {\em SAC}, pp.~1639--1644. ACM, 2011.

\bibitem{kapur}
Deepak Kapur.
\newblock Using Gr\"obner bases to reason about geometry problems.
\newblock {\em Journal of Symbolic Computation}, 2(4), 1986.

\bibitem{projective-coq1}
Nicolas Magaud, Julien Narboux, and Pascal Schreck.
\newblock Formalizing projective plane geometry in coq.
\newblock In {\em Automated Deduction in Geometry} 2008., pages 141--162.

\bibitem{projective-coq2}
Nicolas Magaud, Julien Narboux, and Pascal Schreck.
\newblock A case study in formalizing projective geometry in COQ: Desargues
  theorem.
\newblock {\em Comput. Geom.}, 45(8):406--424, 2012.

\bibitem{thedu}
Filip Mari\'c, Ivan Petrovi\'c, Danijela Petrovi\'c, and Predrag Jani\v{c}i\'c.
\newblock Formalization and implementation of algebraic methods in geometry.
\newblock In {\em THEDU'11}, {\em Electronic Proceedings in Theoretical Computer Science} 79, pp.~63--81. 2012.

\bibitem{hilbert-isabelle}
Laura~I. Meikle and Jacques~D. Fleuriot.
\newblock Formalizing Hilbert's Grundlagen in Isabelle/Isar.
\newblock In {\em TPHOLs}, LNCS 2758, pp.~319--334. Springer, 2003.

\bibitem{narboux}
Julien Narboux.
\newblock Mechanical theorem proving in Tarski's geometry.
\newblock In {\em Automated Deduction in Geometry}, LNCS 4869, pp.~139--156. Springer, 2006.

\bibitem{Isabelle}
Tobias Nipkow, Lawrence~C. Paulson, and Markus Wenzel.
\newblock {\em Isabelle/HOL - A Proof Assistant for Higher-Order Logic}, LNCS 2283.
\newblock Springer, 2002.

\bibitem{coqly}
Tuan-Minh Pham, Yves Bertot, and Julien Narboux.
\newblock A COQ-based library for interactive and automated theorem proving in
  plane geometry.
\newblock In {\em ICCSA (4)}, LNCS 6785, pp.~368--383. Springer, 2011.

\bibitem{grobner_coq}
Lo\"{\i}c Pottier.
\newblock Connecting Gr{\"o}bner bases programs with COQ to do proofs in
  algebra, geometry and arithmetics.
\newblock {\em CoRR}, abs/1007.3615, 2010.

\bibitem{william}
William Richter.
\newblock A minimal version of Hilbert's axioms for plane geometry.
\newblock \url{www.math.northwestern.edu/~richter/hilbert.pdf}

\bibitem{tarski}
W.~Schwabhäuser, W.~Szmielew, and A.~Tarski.
\newblock {\em Metamathematische Methoden in der Geometrie}.
\newblock Springer-Verlag, 1983.

\bibitem{wu}
Wen-Ts\"un Wu.
\newblock On the decision problem and the mechanization of theorem proving in
  elementary geometry.
\newblock {\em Scientia Sinica}, 21, 1978.
\end{thebibliography}


\end{document}
